---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ibkrcp

<!-- badges: start -->
<!-- badges: end -->

`ibkrcp` is a lightweight R client for the [Interactive Brokers Client Portal REST API](https://ibkrcampus.com/campus/ibkr-api-page/cpapi-v1/). It covers session management, account and portfolio queries, market data retrieval, and order placement and cancellation.

## Prerequisites

`ibkrcp` communicates with the IBKR Client Portal Gateway, a lightweight Java process that must be running locally before any function calls are made. The gateway exposes the REST API on `https://localhost:5000`.

1. Download the Client Portal Gateway from the [IBKR API page](https://interactivebrokers.github.io/cpwebapi/quickstart)
2. Start the gateway: `java -jar root/run.jar root/conf.yaml`
3. Log in via the browser prompt at `https://localhost:5000`
4. Confirm the session is live before trading

## Installation

Install the development version from GitHub:

``` r
# install.packages("pak")
pak::pak("sactyr/ibkrcp")
```

## Usage

### Session management

```{r session, eval=FALSE}
library(ibkrcp)

# Confirm the gateway is running and authenticated
ibkr_tickle()

# Check authentication status
ibkr_auth_status()

# Re-authenticate if the session has timed out
ibkr_reauthenticate()
```

### Account and portfolio

```{r account, eval=FALSE}
# Get all accounts
accounts <- ibkr_get_accounts()
account_id <- accounts$account_id[1]

# Portfolio summary (cash balances, net liquidation, etc.)
ibkr_get_summary(account_id)

# Current open positions
ibkr_get_positions(account_id)
```

### Market data

```{r market_data, eval=FALSE}
# Look up a contract ID (conid) by symbol
contracts <- ibkr_search_contracts("VGS")
conid <- contracts$conid[contracts$company_header == "VGS - ASX"]

# OHLCV price history (daily bars, 1 year)
prices <- ibkr_get_price_history(conid, period = "1y")

# ASX trading schedule (trading days, public holidays)
schedule <- ibkr_get_trading_schedule(symbol = "VGS", exchange = "ASX")
```

### Orders

```{r orders, eval=FALSE}
# Place a market order
ibkr_place_order(account_id, conid, side = "BUY", quantity = 10)

# View open orders
ibkr_get_orders()

# Cancel an order
ibkr_cancel_order(account_id, order_id = "1001")
```

## SSL note

The Client Portal Gateway runs on localhost with a self-signed certificate. `ibkrcp` disables SSL peer and host verification for all requests (`ssl_verifypeer = FALSE`, `ssl_verifyhost = FALSE`). This is intentional — verifying SSL against localhost is not meaningful — and follows IBKR's own API guidance.

## Scope and roadmap

`ibkrcp` 0.1.0 covers the endpoints needed for a basic automated trading workflow: 
session management, account queries, market data, and order management. The 
Interactive Brokers Client Portal API is significantly broader than what is 
currently wrapped — real-time streaming, additional order types, transaction 
history, and more remain as future work.

Contributions are welcome. If there's an endpoint you need that isn't covered, 
please open an issue or submit a pull request on 
[GitHub](https://github.com/sactyr/ibkrcp).

## Related

- [IBKR Client Portal API documentation](https://ibkrcampus.com/campus/ibkr-api-page/cpapi-v1/)
- [IBKR Client Portal Gateway download](https://ibkrcampus.com/campus/ibkr-api-page/cpapi-v1/#client-portal-gw)
